implementation quality control

### 2018-03-12 analysis/analyses/4-method_characterisation/7_quality_control.Rmd
add labels for qc categories

check_heatmap_plot <- implementation_qc_checks %>% 
  ggplot() +
    geom_rect(aes(ymax=check_start, ymin=check_end, xmin=as.integer(implementation_id), xmax=as.integer(implementation_id) + 1, fill=category, alpha=answer)) +
  hline_check + hline_aspect +
    geom_vline(aes(xintercept = as.integer(implementation_id)), color="white", alpha=0.2) +
    scale_y_reverse(NULL, breaks = aspect_position$aspect_mid, labels = aspect_position$name, expand = c(0, 0)) +
    # scale_x_continuous("", breaks = seq_along(levels(implementation_qc_checks$implementation_id))+0.5, labels = label_implementation(levels(implementation_qc_checks$implementation_id)), expand = c(0, 0), position="right") +
    scale_x_continuous("", breaks=NULL, expand = c(0, 0)) +
    scale_fill_manual("Category", values=set_names(qc_categories$color, qc_categories$category), label=label_long, guide=guide_legend(ncol=2)) +
    scale_alpha_continuous("Score", guide=guide_legend(ncol=5, label.position = "bottom")) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.text.y = element_text(size=12), legend.position="bottom")

>>>>

check_heatmap_plot <- implementation_qc_checks %>% 
  ggplot() +
    geom_rect(aes(ymax=check_start, ymin=check_end, xmin=as.integer(implementation_id), xmax=as.integer(implementation_id) + 1, fill=category, alpha=answer)) +
  hline_check + hline_aspect +
    geom_vline(aes(xintercept = as.integer(implementation_id)), color="white", alpha=0.2) +
    scale_y_reverse(NULL, breaks = aspect_position$aspect_mid, labels = aspect_position$name, expand = c(0, 0)) +
    # scale_x_continuous("", breaks = seq_along(levels(implementation_qc_checks$implementation_id))+0.5, labels = label_implementation(levels(implementation_qc_checks$implementation_id)), expand = c(0, 0), position="right") +
    scale_x_continuous("", breaks=NULL, expand = c(0, 0)) +
    scale_fill_manual("Category", values=set_names(qc_categories$color, qc_categories$category), labels=set_names(qc_categories$label, qc_categories$category), guide=guide_legend(ncol=2)) +
    scale_alpha_continuous("Score", guide=guide_legend(ncol=5, label.position = "bottom")) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.text.y = element_text(size=12), legend.position="bottom")
